\documentclass[11pt, oneside]{article}
\usepackage{geometry}                		
\geometry{margin=0.75in}
\geometry{letterpaper}                   		
							
\usepackage{amssymb}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\title{Local Mobile App Requirements & Features}
\author{Lucas Bearden & Jordan Taylor}

\begin{document}
\maketitle
The app that we will be creating is called Local. It will be an app that will recommend Local entertainment, restuarants, markets, and shops. Users will have their own local city, and will be able to rate local establishments and vote on whether they consider them to be local or not. Users will also become more local the more their reviews are viewed, and a ranking system will be employed to rank the most local users for given cities. The app will integrate with Facebook to grab a user's hometown and make that their first ``local city''. The app will also integrate with Google Maps to pin the locations of the local things. Users will also be able to favorite local items, and make an intenerary of things they would like to do. 

Our app does have its number of risks. One of the big risks is the scope of the project. While we have a quite well-developed idea, it is large, with many different features. Another risk is our use of APIs, we do not have a ton of exprience integerating with other software APIs and we are planning on using at least the Facebook and Google Maps APIs.
\begin{itemize}
   \item Must-have features:
       \begin{itemize}
          \item Individual user accounts, can be created with Facebook/Google account.
          \item Google Maps integration to show locations.
          \item Review and rating system.
          \item Categories of items i.e., Entertainment, Food, Markets, Shops.
          \item Users can have multiple ``Local cities''.
          \item User rating system to rank who is the most local for each city (locality rating).
          \item Itinerary (My List)
       \end{itemize}  
   \item Nice to-have features:
       \begin{itemize}
          \item ``Tonight'' featuring specials that are around you for that night and upcoming nights.
          \item Integration with apps such as Yelp etc. to share reviews.
          \item Method for users to add their own Local items.
          \item Favorite cities list.
       \end{itemize}
  \end{itemize}
\end{document}  